---
title: "Simultaneous inference with SILM"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simultaneous inference with SILM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

SILM provides simultaneous inference for the high-dimensional linear model
$Y = X\beta + \epsilon$, based on the de-biased (de-sparsified) lasso and the
bootstrap. It implements two closely related papers:

* **Zhang and Cheng (2017, JASA)** bootstrap the *linear part* of the de-biased
  lasso with Gaussian multipliers: simultaneous confidence intervals
  (`Sim.CI()`), support recovery (`SR()`), testing for sparse signals (`ST()`)
  and stepdown multiple testing (`Step()`).
* **Dezeure, Bühlmann and Zhang (2017, TEST)** bootstrap the *entire*
  de-sparsified lasso (`boot.lasso.proj()`): residual, wild (Gaussian or
  Mammen multipliers) or xyz-paired bootstrap, robust standard errors,
  Westfall–Young multiple testing, simultaneous confidence intervals and group
  tests.

The examples below use small dimensions so that the vignette builds quickly;
the methods are intended for large $p$.

```{r}
library(SILM)
set.seed(1)
n <- 100
p <- 60
Sigma <- 0.9^abs(outer(1:p, 1:p, "-"))            # Toeplitz design
X <- matrix(rnorm(n * p), n, p) %*% chol(Sigma)
beta <- c(1.5, -1, 2, rep(0, p - 3))
Y <- as.vector(X %*% beta + rt(n, 4) / sqrt(2))
```

The model has no intercept. The data above have mean zero; for real data use
`center = TRUE` (or centre the data beforehand).

## Zhang and Cheng (2017)

Here $p > n/2$, so the matrix $\Theta$ (the inverse of the population Gram
matrix) is estimated by the nodewise lasso. It depends only on the design and
can be computed once:

```{r}
Theta <- Theta.hat(X)
```

Simultaneous 95% confidence intervals for $\beta_1, \dots, \beta_5$ (note that
`alpha` is the *confidence level* in `Sim.CI()`):

```{r}
ci <- Sim.CI(X, Y, set = 1:5, M = 500, alpha = 0.95, Theta = Theta)
ci$band.st
```

Support recovery and stepdown multiple testing at familywise level 5%:

```{r}
SR(X, Y, Theta = Theta)
Step(X, Y, M = 500, alpha = 0.05, Theta = Theta)
```

Testing whether any of the variables 4 to 60 has a non-zero coefficient, with
a screening sub-sample of size $0.3n$:

```{r}
ST(X, Y, sub.size = 0.3, test.set = 4:p, M = 500)[c(3, 4)]
```

## Dezeure, Bühlmann and Zhang (2017)

`boot.lasso.proj()` bootstraps the entire estimator. The paper recommends the
robust standard error and, for heteroscedastic errors, the wild bootstrap.
`boot.shortcut = TRUE` refits the bootstrap lasso at the original tuning
parameter, which is much faster.

```{r}
fit <- boot.lasso.proj(X, Y, B = 200, robust = TRUE, wild = TRUE,
                       boot.shortcut = TRUE, return.bootdist = TRUE)
fit
```

Individual and simultaneous confidence intervals:

```{r}
confint(fit, parm = 1:5)
confint(fit, type = "simultaneous", group = 1:5)
```

Group tests of $H_{0,G}: \beta_j = 0$ for all $j \in G$:

```{r}
groupTest(fit, list(signal = 1:3, noise = 4:p))
```

Mammen multipliers and the xyz-paired bootstrap are selected with
`multiplier = "mammen"` and `boot.type = "xyz"`.

`lasso.proj()` computes the de-sparsified lasso with asymptotic Gaussian
p-values and intervals (the "original" estimator of the paper):

```{r}
lp <- lasso.proj(X, Y, robust = TRUE)
confint(lp, parm = 1:3)
```

## Two bootstraps

`Sim.CI()` bootstraps only the linear part $\hat\Theta X^\top \epsilon / n$
of the de-biased lasso, which is fast and needs no refitting. `boot.lasso.proj()`
refits the lasso for every bootstrap sample. Dezeure, Bühlmann and Zhang (2017)
found that the latter often has better finite-sample coverage. It also handles
heteroscedastic errors (with the wild bootstrap and robust standard errors).
Their default nodewise tuning also differs: `Sim.CI()` uses the Z&Z rule
(`nodewise = "ZnZ"`), while `boot.lasso.proj()` keeps hdi's cross-validated
lambda (`do.ZnZ = FALSE`).

## Reproducing results of the archived versions

SILM 2.0.0 reproduces the archived SILM 1.0.0 and hdi 0.1-10 exactly (the
same numbers under the same random seed):

* `SR()`, `Sim.CI()`, `Step()`, `ST()`: results obtained with SILM 1.0.0 and
  hdi 0.1-7 to 0.1-10 (March 2019 to July 2026) are the default
  (`nodewise = "ZnZ"`, chosen by a pre-registered simulation study; see
  `?SR`). Results obtained with hdi 0.1-6 (January to March 2019) need
  `nodewise = "cv"`, the tuning described in Zhang and Cheng (2017). For
  `ST()`, `legacy = TRUE` also restores three behaviours of SILM 1.0.0 that
  were corrected (see `?ST`).
* `lasso.proj()`, `boot.lasso.proj()`: identical to hdi 0.1-10, except for
  `lasso.proj(family = "binomial")`, where hdi's results need
  `legacy = TRUE`.
* Results computed with R < 3.6.0 used a different random sampling
  algorithm: call `RNGkind(sample.kind = "Rounding")` before `set.seed()`.

The equivalence is verified continuously against the archived CRAN packages
(see the `validation/` directory of the source repository).

## References

Zhang, X. and Cheng, G. (2017). Simultaneous inference for high-dimensional
linear models. *Journal of the American Statistical Association*, 112,
757–768.

Dezeure, R., Bühlmann, P. and Zhang, C.-H. (2017). High-dimensional
simultaneous inference with the bootstrap. *TEST*, 26, 685–719.

Dezeure, R., Bühlmann, P., Meier, L. and Meinshausen, N. (2015).
High-dimensional inference: confidence intervals, p-values and R-software hdi.
*Statistical Science*, 30, 533–558.
